%=============================================================================================
%                                     Chapter 7: References
%=============================================================================================

\chapter*{References}
\addcontentsline{toc}{chapter}{References}

\begin{thebibliography}{99}

\bibitem{SchrodingerE35}
E. Schrödinger, ``Discussion of probability relations between separated systems,'' \textit{Mathematical Proceedings of the Cambridge Philosophical Society}, vol. 31, no. 4, pp. 555--563, 1935.

\bibitem{einsteinPodolskyRosen1935}
A. Einstein, B. Podolsky, and N. Rosen, ``Can quantum-mechanical description of physical reality be considered complete?,'' \textit{Physical Review}, vol. 47, no. 10, pp. 777--780, 1935.

\bibitem{BranciardC12}
C. Branciard, E. G. Cavalcanti, S. P. Walborn, V. Scarani, and H. M. Wiseman, ``One-sided device-independent quantum key distribution: Security, feasibility, and the connection with steering,'' \textit{Physical Review A}, vol. 85, no. 1, p. 010301(R), 2012.

\bibitem{WisemanH07}
H. M. Wiseman, S. J. Jones, and A. C. Doherty, ``Steering, entanglement, nonlocality, and the Einstein-Podolsky-Rosen paradox,'' \textit{Physical Review Letters}, vol. 98, no. 14, p. 140402, 2007.

\bibitem{WeedbrookC12}
C. Weedbrook, S. Pirandola, R. García-Patrón, N. J. Cerf, T. C. Ralph, J. H. Shapiro, and S. Lloyd, ``Gaussian quantum information,'' \textit{Reviews of Modern Physics}, vol. 84, no. 2, p. 621, 2012.

\bibitem{Qamar2008}
S. Qamar, F. Ghafoor, M. Hillery, and M. S. Zubairy, ``Quantum beat laser as a source of entangled radiation,'' \textit{Physical Review A}, vol. 77, no. 6, p. 062308, 2008.

\bibitem{Scully1997}
M. O. Scully and M. S. Zubairy, \textit{Quantum Optics}. Cambridge: Cambridge University Press, 1997.

\bibitem{Qamar2009}
S. Qamar, S. Al-Amri, and M. S. Zubairy, ``Entangled radiation via a Raman-driven quantum-beat laser,'' \textit{Physical Review A}, vol. 80, no. 3, p. 033818, 2009.

\bibitem{Zubairy1992}
M. S. Zubairy, M. O. Scully, and J. H. Eberly, ``Directional spontaneous emission from an extended ensemble of N atoms: Cooperation and disorder,'' \textit{Physical Review A}, vol. 36, no. 6, p. 2519, 1992.

\bibitem{ShakirUllah19}
S. Ullah, H. S. Qureshi, and F. Ghafoor, ``Coherence control of entanglement dynamics of two-mode Gaussian state via Raman driven quantum beat laser using Simon's criterion,'' \textit{Applied Optics}, vol. 58, no. 2, pp. 197--204, 2019.

\bibitem{RaiDasAgarwal2010}
A. Rai, S. Das, and G. S. Agarwal, ``Quantum entanglement in coupled lossy waveguides,'' \textit{Optics Express}, vol. 18, no. 6, pp. 6241--6254, 2010.

\bibitem{UllahQureshiGhafoor2019}
S. Ullah, H. S. Qureshi, and F. Ghafoor, ``Hierarchy of temporal quantum correlations using a correlated spontaneous emission laser,'' \textit{Optics Express}, vol. 27, no. 19, pp. 26858--26873, 2019.

\bibitem{kogiastQuantificationGaussianQuantum2015}
I. Kogias, A. R. Lee, S. Ragy, and G. Adesso, ``Quantification of Gaussian quantum steering,'' \textit{Physical Review Letters}, vol. 114, no. 6, p. 060403, 2015.

\bibitem{brunnerBellNonlocality2014}
N. Brunner, D. Cavalcanti, S. Pironio, V. Scarani, and S. Wehner, ``Bell nonlocality,'' \textit{Reviews of Modern Physics}, vol. 86, no. 2, p. 419, 2014.

\bibitem{PolitiSilicaonSilicon2008}
A. Politi, M. J. Cryan, J. G. Rarity, S. Yu, and J. L. O'Brien, ``Silica-on-silicon waveguide quantum circuits,'' \textit{Science}, vol. 320, no. 5876, pp. 646--649, 2008.

\bibitem{laiNonclassicalFieldsLinear1991}
W. K. Lai, V. Bužek, and P. L. Knight, ``Nonclassical fields in a linear directional coupler,'' \textit{Physical Review A}, vol. 43, no. 12, p. 6323, 1991.

\bibitem{downlingQuantumTechnology2003}
J. P. Dowling and G. J. Milburn, ``Quantum technology: the second quantum revolution,'' \textit{Philosophical Transactions of the Royal Society A: Mathematical, Physical and Engineering Sciences}, vol. 361, no. 1809, pp. 1655--1674, 2003.

\bibitem{VidalWerner2002}
G. Vidal and R. F. Werner, ``Computable measure of entanglement,'' \textit{Physical Review A}, vol. 65, no. 3, p. 032314, 2002.

\bibitem{AdessoDatta2010}
G. Adesso and A. Datta, ``Quantum versus classical correlations in Gaussian states,'' \textit{Physical Review Letters}, vol. 105, no. 3, p. 030501, 2010.

\bibitem{GiordaParis2010}
P. Giorda and M. G. A. Paris, ``Gaussian quantum discord,'' \textit{Physical Review Letters}, vol. 105, no. 20, p. 020503, 2010.

\bibitem{OlivierZurek2001}
H. Ollivier and W. H. Zurek, ``Quantum discord: a measure of the quantumness of correlations,'' \textit{Physical Review Letters}, vol. 88, no. 1, p. 017901, 2001.

\bibitem{HorodockiHorodocki2009}
R. Horodecki, P. Horodecki, M. Horodecki, and K. Horodecki, ``Quantum entanglement,'' \textit{Reviews of Modern Physics}, vol. 81, no. 2, p. 865, 2009.

\bibitem{ModiBrodutch2012}
K. Modi, A. Brodutch, H. Cable, T. Paterek, and V. Vedral, ``The classical-quantum boundary for correlations: Discord and related measures,'' \textit{Reviews of Modern Physics}, vol. 84, no. 4, p. 1655, 2012.

\bibitem{DuanGiedke2000}
L.-M. Duan, G. Giedke, J. I. Cirac, and P. Zoller, ``Inseparability criterion for continuous variable systems,'' \textit{Physical Review Letters}, vol. 84, no. 12, p. 2722, 2000.

\bibitem{SimonPeres2000}
R. Simon, ``Peres-Horodecki separability criterion for continuous variable systems,'' \textit{Physical Review Letters}, vol. 84, no. 12, p. 2726, 2000.

\bibitem{BarnettRadmore2002}
S. M. Barnett and P. M. Radmore, \textit{Methods in Theoretical Quantum Optics}. Oxford: Oxford University Press, 2002.

\bibitem{BraunsteinVanLoock2005}
S. L. Braunstein and P. van Loock, ``Quantum information with continuous variables,'' \textit{Reviews of Modern Physics}, vol. 77, no. 2, p. 513, 2005.

\end{thebibliography}

